SCM plan for a troubling company

### 2012-01-11 article.tex
ignet
some changes

\begin{abstract}
Many companies, especially the small ones, don't see the benefits of SCM in their company and decides to not use it.
This company however have now seen the light and need help to implement it.
This report goes through some aspects in this implementation and focus on a relatively small software company of 40-50 employees.
We analyze some of their problems and come up with solutions in the form of a configuration plan.
\end{abstract}
\newpage

@@

The company that should have SCM implemented will be referred to as ''The Problem Company'' throughout the report.
It is a small company, 12 employees which have grown in the past few years and intends to keep growing in the future.
The current size is about 40-50 employees and develops software to a local cellphone company.

@@

The company are programming Java and are using Eclipse as their tool.

@@

The configuration identification for the software part is quite straightforward where every module is it's own configuration item and can be subdivided in the files as the next step of the hierarchy.
For the files the filenames and their directories provides a natural naming and an SCM-tool makes this easy to keep track of. The various modules are then combined and this can be kept in the tool as well or be managed manually.
As the documentation actually is tied to the code and it's versions it should, if possible be controlled in the same system to keep it in sync with the code.
The next higher level of configutration control needed is the release level where the build environment and the actual produced binaries together with the released documentation.
This also needs to be documented and controlled in some way as the released models are supported for some years at least.

\subsection{Other items}

As the delivered product is in form of binaries and documentation for inclusion in a larger product there is not much other releasables to control.
However to structure the change process and design of new features design and specification documents are created for communication between customer and the company as well as between internal designers and the coders. These needs to be versioned and saved as well to be able to verify that the product performs according to the specifications.

@@

\subsection{The change process}
The main idea behind configuration control is to achieve control of changes, what impact they'll have and their costs.

>>>>

\begin{abstract}

Many companies, especially the small ones, don't see the benefits of SCM in their company and decides to not use it.
This company however have now seen the light and need help to implement it.
This report goes through some aspects in this implementation and focus on a relatively small software company of 40-50 employees.
We analyze some of their problems and come up with solutions in the form of a configuration plan.

\end{abstract}
\newpage

@@

The company that should have SCM implemented will be referred to as ''The Problem Company'' throughout the report.
It is a small company, 12 employees which have grown in the past few years and intends to keep growing in the future.
The current size is about 40-50 employees and develops software to a local cellphone company. 
The Problem Company is located in Lund and has no plans on moving or expand to other cities. Therefore all who works in the project are located in the same building, however the customer is located in a neighboring building and needs to have good contact with them.

@@

The company are programming Java and are using Eclipse as their tool.
Since the beginning they have used traditional programming instead of agile and are well familiar and comfortable with it.

@@

Kanske lite diagram visande CI

Binären måste kontrolleras, dokumentation i versionskontroll också
Design dokument, diagram måste numreras/hanteras

Since we will be implementing the SCM plan iteratively we will start off with some baselines.

-documentation

-source code
Levereras som binär + dokumentation.
Mjukvara har inbyggd ``labelling''

\subsection{Version control}
Med lämplig mjukvara för kod + dokumentation.
Design dokument binära och hanterasw av icke-kodare (akm) bättre med central filserver+versionsnummer manuellt.

@@

The main idea behind configuration control is to achieve control of changes, what impact they'll have and their costs.
